---
title: "Analysis 2"
author: "Johannes Nakayama"
date: "16 11 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(arrow)
library(here)
library(magrittr)
library(ggpubr)
library(agrmt)
source("helpers.R")
SAVE <- TRUE  # set TRUE if you want to save the plots
COLOR <- "firebrick"
BATCH_NAME <- "expanding_square"
if (!("figures" %in% list.files()) & SAVE) {dir.create("figures", showWarnings = FALSE)}
```

## Data

```{r}
batchruns <- character()
for (filename in list.files(here::here("..", "data", BATCH_NAME))) {
  varname <- stringr::str_remove(filename, ".feather")
  
  if (!grepl("configs", varname)) {
    batchruns <- append(batchruns, varname)
    assign(varname, arrow::read_feather(here::here("..", "data", BATCH_NAME, filename))) 
    assign(varname, format_data(eval(as.symbol(varname))))
  }  
}

arrow::read_feather(here::here("..", "data", BATCH_NAME, "configs.feather")) %>% 
  sapply(as.numeric) %>% 
  as_tibble() -> config


config[,-(1:2)] %<>% map_df(as.factor)

```


## Distribution

```{r}
# generics ----
binwidth <- 1

# plotting ----

distribution_plots <- list()

for (i in 1:length(batchruns)) {
  distribution_plots[[i]] <- distribution_plot(
  dataset = get(batchruns[i]), title = batchruns[i], binwidth = binwidth, color = COLOR
  )
}

ggarrange(
  plotlist = distribution_plots,
  ncol = ceiling(sqrt(length(batchruns))), nrow = floor(sqrt(length(batchruns)))
) +
  theme_axelfraud_arrange()

# saving ----
if(SAVE){ggsave(filename = here::here("figures", "distribution.png"), width = 10, height = 10, dpi = 300)}
```


## Development of Cultures

```{r}
# generics ----
alpha <- 0.05
size <- 2

# plotting ----

development_plots <- list()

for (i in 1:length(batchruns)) {
  development_plots[[i]] <- development_plot(
  dataset = get(batchruns[i]), title = batchruns[i], alpha = alpha, size = size, color = COLOR
  )
}


ggarrange(
  plotlist = development_plots,
  ncol = ceiling(sqrt(length(batchruns))), nrow = floor(sqrt(length(batchruns)))
) +
  theme_axelfraud_arrange()

# saving ----
if(SAVE){ggsave(filename = here::here("figures", "development.png"), width = 10, height = 10, dpi = 300)}
```


```{r}
# generics ----
alpha <- 0.05
size <- 2
binwidth <- 1

# create grid plots and list of all plots in correct order ----
all_plots <- list()

for (i in 1:length(batchruns)) {
  grid_plots[[i]] <- config %>% grid_plot(x = "x", y = "y", color = batchruns[i])
  
  all_plots[[length(all_plots) + 1]] <- grid_plots[[i]]
  all_plots[[length(all_plots) + 1]] <- development_plots[[i]]
  all_plots[[length(all_plots) + 1]] <- distribution_plots[[i]]
}


# arrange and save plots ----
ggarrange(
  plotlist = all_plots,
  ncol = 3, nrow = 5
) +
  theme_axelfraud_arrange(plot_margin = 15)

if(SAVE){ggsave(filename = here::here("figures", "full_visual_analysis_a.png"), width = 14, height = 14, dpi = 300)}
```



```{r, eval=FALSE}
# for powerpoint ----
library(scales)
show_col(grey_pal(0, 1)(10))
grDevices::col2rgb("grey40")
```


```{r, eval=FALSE}
line_edge %>% by_class("line_edge") %>% 
  rbind(line_center %>% by_class("line_center")) %>% 
  rbind(square_corner %>% by_class("square_corner")) %>% 
  rbind(square_center %>% by_class("square_center")) %>% 
  rbind(random %>% by_class("random")) %>% 
  rbind(corners %>% by_class("corners")) %>% 
  rbind(diagonal %>% by_class("diagonal")) %>% 
  rbind(distance_center %>% by_class("distance_center")) -> tmp

tmp %>% 
  group_by(config) %>% 
  summarize(
    agreement = agreement(count),
    polarization = polarization(count),
    consensus = consensus(count),
    BerryMielke = BerryMielke(count),
    BlairLacy = BlairLacy(count)
  ) %>% 
  ungroup()

```

```{r}
# compute agreements over time ----
square_corner %>% agreement_by_step() -> square_corner_agreement
square_center %>% agreement_by_step() -> square_center_agreement
corners %>% agreement_by_step() -> corners_agreement
line_edge %>% agreement_by_step() -> line_edge_agreement
line_center %>% agreement_by_step() -> line_center_agreement
diagonal %>% agreement_by_step() -> diagonal_agreement
distance_center %>% agreement_by_step() -> distance_center_agreement
random %>% agreement_by_step() -> random_agreement

# plotting ----
square_corner_agreement %>% 
  ggplot(aes(x = step, y = agreement)) +
    geom_hline(yintercept = 0, size = 1.5, color = "grey40") +
    geom_line(size = 2, alpha = 0.7, color = COLOR) +
    scale_y_continuous(limits = c(-1, 1)) +
    labs(title = "Square corner", x = "Step", y = "Agreement") +
    theme_axelfraud() +
    theme(axis.title = element_text(size = 12)) -> square_corner_agreement_plot

square_center_agreement %>% 
  ggplot(aes(x = step, y = agreement)) +
    geom_hline(yintercept = 0, size = 1.5, color = "grey40") +
    geom_line(size = 2, alpha = 0.7, color = COLOR) +
    scale_y_continuous(limits = c(-1, 1)) +
    labs(title = "Square center", x = "Step", y = "Agreement") +
    theme_axelfraud() +
    theme(axis.title = element_text(size = 12)) -> square_center_agreement_plot

corners_agreement %>% 
  ggplot(aes(x = step, y = agreement)) +
    geom_hline(yintercept = 0, size = 1.5, color = "grey40") +
    geom_line(size = 2, alpha = 0.7, color = COLOR) +
    scale_y_continuous(limits = c(-1, 1)) +
    labs(title = "Corners", x = "Step", y = "Agreement") +
    theme_axelfraud() +
    theme(axis.title = element_text(size = 12)) -> corners_agreement_plot

line_edge_agreement %>% 
  ggplot(aes(x = step, y = agreement)) +
    geom_hline(yintercept = 0, size = 1.5, color = "grey40") +
    geom_line(size = 2, alpha = 0.7, color = COLOR) +
    scale_y_continuous(limits = c(-1, 1)) +
    labs(title = "Line edge", x = "Step", y = "Agreement") +
    theme_axelfraud() +
    theme(axis.title = element_text(size = 12)) -> line_edge_agreement_plot

line_center_agreement %>% 
  ggplot(aes(x = step, y = agreement)) +
    geom_hline(yintercept = 0, size = 1.5, color = "grey40") +
    geom_line(size = 2, alpha = 0.7, color = COLOR) +
    scale_y_continuous(limits = c(-1, 1)) +
    labs(title = "Line center", x = "Step", y = "Agreement") +
    theme_axelfraud() +
    theme(axis.title = element_text(size = 12)) -> line_center_agreement_plot

diagonal_agreement %>% 
  ggplot(aes(x = step, y = agreement)) +
    geom_hline(yintercept = 0, size = 1.5, color = "grey40") +
    geom_line(size = 2, alpha = 0.7, color = COLOR) +
    scale_y_continuous(limits = c(-1, 1)) +
    labs(title = "Diagonal", x = "Step", y = "Agreement") +
    theme_axelfraud() +
    theme(axis.title = element_text(size = 12)) -> diagonal_agreement_plot

distance_center_agreement %>% 
  ggplot(aes(x = step, y = agreement)) +
    geom_hline(yintercept = 0, size = 1.5, color = "grey40") +
    geom_line(size = 2, alpha = 0.7, color = COLOR) +
    scale_y_continuous(limits = c(-1, 1)) +
    labs(title = "Distance center", x = "Step", y = "Agreement") +
    theme_axelfraud() +
    theme(axis.title = element_text(size = 12)) -> distance_center_agreement_plot

random_agreement %>% 
  ggplot(aes(x = step, y = agreement)) +
    geom_hline(yintercept = 0, size = 1.5, color = "grey40") +
    geom_line(size = 2, alpha = 0.7, color = COLOR) +
    scale_y_continuous(limits = c(-1, 1)) +
    labs(title = "Random", x = "Step", y = "Agreement") +
    theme_axelfraud() +
    theme(axis.title = element_text(size = 12)) -> random_agreement_plot

# arrange plots and save ----
ggarrange(
  random_agreement_plot, distance_center_agreement_plot, diagonal_agreement_plot, line_edge_agreement_plot, 
  ncol = 1, nrow = 4
)

if(SAVE){ggsave(filename = here::here("figures", "agreement_over_time_a.png"), width = 7, height = 10, dpi = 300)}

ggarrange(
  line_center_agreement_plot, square_corner_agreement_plot, square_center_agreement_plot, corners_agreement_plot,
  ncol = 1, nrow = 4
)

if(SAVE){ggsave(filename = here::here("figures", "agreement_over_time_b.png"), width = 7, height = 10, dpi = 300)}
```



# Measurements

shortterm:

  * van der Eijk's A (measurement of agreement)
  * refer to https://en.wikipedia.org/wiki/Multimodal_distribution for other measurements  
  * stubborn threshold value? (at some point -> stubborn culture wins?)
  * fit logistic curve to different replicates -> find turning point
  * activity parameter (comparison with last step)
  * agrmt package -> other measures

longterm:
  
  * manipulate stubborn count
  * other network types
  * informed agents
  * interval scale for cultures
  * neighbor count of stubborn agents (random -> expected value / combinatorics)



## Unique Cultures

```{r, eval=FALSE}
color_scheme <- viridis(300, option = "plasma")
color_scheme2 <- rep(COLOR, 300)

data %>% 
  group_by(step, replicate, culture) %>% 
  summarize(count = n()) %>% 
  ungroup() %>% 
  group_by(step, replicate) %>% 
  summarize(unique_cultures = n()) %>% 
  ungroup() -> tmp

tmp %>% 
  ggplot(aes(x = step, y = unique_cultures, color = as.factor(replicate))) +
  geom_line(alpha = 0.05, size = 2) +
  scale_color_manual(values = color_scheme2) +
  labs(
    title = "Development of unique culture count",
    x = "Step",
    y = "Unique cultures"
  ) +
  theme(legend.position = "None") +
  theme_axelfraud()

if(SAVE){ggsave(filename = "unique_cultures.png", width = 10, height = 4, dpi = 300)}
```
























