---
title: "Exploratory Analysis"
author: "Johannes Nakayama"
date: "3 11 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(arrow)
library(here)
library(magrittr)
library(ggpubr)
source("helpers.R")
SAVE <- TRUE  # set TRUE if you want to save the plots
COLOR <- "firebrick"
if (!("figures" %in% list.files()) & SAVE) {dir.create("figures", showWarnings = FALSE)}
```

## Data

```{r}
# read datasets ----
baseline <- load_data(here::here("..", "data", "baseline.feather"))
corners <- load_data(here::here("..", "data", "corners.feather"))
diagonal <- load_data(here::here("..", "data", "diagonal.feather"))
distance_center <- load_data(here::here("..", "data", "distance_center.feather"))
line_center <- load_data(here::here("..", "data", "line_center.feather"))
line_edge <- load_data(here::here("..", "data", "line_edge.feather"))
random <- load_data(here::here("..", "data", "random.feather"))
square_center <- load_data(here::here("..", "data", "square_center.feather"))
square_corner <- load_data(here::here("..", "data", "square_corner.feather"))
```


## Distribution

```{r}
# generics ----
binwidth <- 1

# plotting ----
corners_distribution <- distribution_plot(
  dataset = corners, title = "Corners", binwidth = binwidth, color = COLOR
)
diagonal_distribution <- distribution_plot(
  dataset = diagonal, title = "Diagonal", binwidth = binwidth, color = COLOR
)
distance_center_distribution <- distribution_plot(
  dataset = distance_center, title = "Distance center", binwidth = binwidth, color = COLOR
)
line_center_distribution <- distribution_plot(
  dataset = line_center, title = "Line center", binwidth = binwidth, color = COLOR
)
line_edge_distribution <- distribution_plot(
  dataset = line_edge, title = "Line edge", binwidth = binwidth, color = COLOR
)
random_distribution <- distribution_plot(
  dataset = random, title = "Random", binwidth = binwidth, color = COLOR
)
square_center_distribution <- distribution_plot(
  dataset = square_center, title = "Square center", binwidth = binwidth, color = COLOR
)
square_corner_distribution <- distribution_plot(
  dataset = square_corner, title = "Square corner", binwidth = binwidth, color = COLOR
)

ggarrange(
  corners_distribution, diagonal_distribution, distance_center_distribution, line_center_distribution, 
  line_edge_distribution, random_distribution, square_center_distribution, square_corner_distribution,
  ncol = 2, nrow = 4
) +
  theme_axelfraud_arrange()

# saving ----
if(SAVE){ggsave(filename = here::here("figures", "distribution.png"), width = 10, height = 10, dpi = 300)}
```


# Development of Cultures

```{r}
# generics ----
alpha <- 0.05
size <- 2

# plotting ----
corners_development <- development_plot(
  dataset = corners, title = "Corners", alpha = alpha, size = size, color = COLOR
)
diagonal_development <- development_plot(
  dataset = diagonal, title ="Diagonal", alpha = alpha, size = size, color = COLOR
)
distance_center_development <- development_plot(
  dataset = distance_center, title = "Distance center", alpha = alpha, size = size, color = COLOR
)
line_center_development <- development_plot(
  dataset = line_center, title = "Line center", alpha = alpha, size = size, color = COLOR
)
line_edge_development <- development_plot(
  dataset = line_edge, title = "Line edge", alpha = alpha, size = size, color = COLOR
)
random_development <- development_plot(
  dataset = random, title = "Random", alpha = alpha, size = size, color = COLOR
)
square_center_development <- development_plot(
  dataset = square_center, title = "Square center", alpha = alpha, size = size, color = COLOR
)
square_corner_development <- development_plot(
  dataset = square_corner, title = "Square corner", alpha = alpha, size = size, color = COLOR
)

ggarrange(
  corners_development, diagonal_development, distance_center_development, line_center_development,
  line_edge_development, random_development, square_center_development, square_corner_development,
  ncol = 2, nrow = 4
) +
  theme_axelfraud_arrange()

# saving ----
if(SAVE){ggsave(filename = here::here("figures", "development.png"), width = 10, height = 10, dpi = 300)}
```

```{r, eval=FALSE}
library(agrmt)

random %>% 
  filter(step == max(step)) %>% 
  filter(culture == "00000") %>% 
  group_by(replicate) %>% 
  summarize(stubborn_culture_count = n()) %>% 
  ungroup() %>% 
  mutate(stubborn_culture_grouped = ceiling(stubborn_culture_count / 10)) %>% 
  group_by(stubborn_culture_grouped) %>% 
  summarize(count = n()) %>% 
  ungroup() %>% 
  mutate(count = as.numeric(count)) -> tmp

agreement(tmp$count)
polarization(tmp$count)
consensus(tmp$count)
consensus.variance(tmp$count)
concentration(tmp$count)
BerryMielke(tmp$count)
BlairLacy(tmp$count)
lsquared(tmp$count)
lsquared.variance(tmp$count)
l.variance(tmp$count)
dispersion(tmp$count)
Reardon(tmp$count)
entropy(tmp$count)
Leik(tmp$count)
ajus(tmp$count)
ajusPlot(tmp$count)


```



# Measurements

shortterm:

  * van der Eijk's A (measurement of agreement)
  * refer to https://en.wikipedia.org/wiki/Multimodal_distribution for other measurements  
  * stubborn threshold value? (at some point -> stubborn culture wins?)
  * fit logistic curve to different replicates -> find turning point
  * activity parameter (comparison with last step)
  * van der Eijk's A for every step -> plot
  * correct implementation of random configuration
  * agrmt package -> other measures

longterm:
  
  * manipulate stubborn count
  * other network types
  * informed agents
  * interval scale for cultures



# Unique Cultures

```{r, eval=FALSE}
color_scheme <- viridis(300, option = "plasma")
color_scheme2 <- rep(COLOR, 300)

data %>% 
  group_by(step, replicate, culture) %>% 
  summarize(count = n()) %>% 
  ungroup() %>% 
  group_by(step, replicate) %>% 
  summarize(unique_cultures = n()) %>% 
  ungroup() -> tmp

tmp %>% 
  ggplot(aes(x = step, y = unique_cultures, color = as.factor(replicate))) +
  geom_line(alpha = 0.05, size = 2) +
  scale_color_manual(values = color_scheme2) +
  labs(
    title = "Development of unique culture count",
    x = "Step",
    y = "Unique cultures"
  ) +
  theme(legend.position = "None") +
  theme_axelfraud()

if(SAVE){ggsave(filename = "unique_cultures.png", width = 10, height = 4, dpi = 300)}
```
























