---
title: "Exploratory Analysis"
author: "Johannes Nakayama"
date: "3 11 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(arrow)
library(here)
library(magrittr)
library(ggpubr)
library(agrmt)
source("helpers.R")
SAVE <- TRUE  # set TRUE if you want to save the plots
COLOR <- "firebrick"
if (!("figures" %in% list.files()) & SAVE) {dir.create("figures", showWarnings = FALSE)}
```

## Data

```{r}
# read simulation datasets ----
baseline <- load_data(here::here("..", "data", "baseline.feather"))
corners <- load_data(here::here("..", "data", "corners.feather"))
diagonal <- load_data(here::here("..", "data", "diagonal.feather"))
distance_center <- load_data(here::here("..", "data", "distance_center.feather"))
line_center <- load_data(here::here("..", "data", "line_center.feather"))
line_edge <- load_data(here::here("..", "data", "line_edge.feather"))
random <- load_data(here::here("..", "data", "random.feather"))
square_center <- load_data(here::here("..", "data", "square_center.feather"))
square_corner <- load_data(here::here("..", "data", "square_corner.feather"))

# read grid outlines ----
grid_df <- read_delim(here::here("..", "data", "grid_data.csv"), delim = ";") %>% 
  mutate(
    x = as.numeric(x),
    y = as.numeric(y),
    line_edge = as.factor(line_edge),
    line_center = as.factor(line_center),
    square_corner = as.factor(square_corner),
    square_center = as.factor(square_center),
    random = as.factor(random),
    corners = as.factor(corners),
    diagonal = as.factor(diagonal),
    distance_center = as.factor(distance_center)
  )
```


## Distribution

```{r}
# generics ----
binwidth <- 1

# plotting ----
corners_distribution <- distribution_plot(
  dataset = corners, title = "Corners", binwidth = binwidth, color = COLOR
)
diagonal_distribution <- distribution_plot(
  dataset = diagonal, title = "Diagonal", binwidth = binwidth, color = COLOR
)
distance_center_distribution <- distribution_plot(
  dataset = distance_center, title = "Distance center", binwidth = binwidth, color = COLOR
)
line_center_distribution <- distribution_plot(
  dataset = line_center, title = "Line center", binwidth = binwidth, color = COLOR
)
line_edge_distribution <- distribution_plot(
  dataset = line_edge, title = "Line edge", binwidth = binwidth, color = COLOR
)
random_distribution <- distribution_plot(
  dataset = random, title = "Random", binwidth = binwidth, color = COLOR
)
square_center_distribution <- distribution_plot(
  dataset = square_center, title = "Square center", binwidth = binwidth, color = COLOR
)
square_corner_distribution <- distribution_plot(
  dataset = square_corner, title = "Square corner", binwidth = binwidth, color = COLOR
)

ggarrange(
  corners_distribution, diagonal_distribution, distance_center_distribution, line_center_distribution, 
  line_edge_distribution, random_distribution, square_center_distribution, square_corner_distribution,
  ncol = 2, nrow = 4
) +
  theme_axelfraud_arrange()

# saving ----
if(SAVE){ggsave(filename = here::here("figures", "distribution.png"), width = 10, height = 10, dpi = 300)}
```


## Development of Cultures

```{r}
# generics ----
alpha <- 0.05
size <- 2

# plotting ----
corners_development <- development_plot(
  dataset = corners, title = "Corners", alpha = alpha, size = size, color = COLOR
)
diagonal_development <- development_plot(
  dataset = diagonal, title ="Diagonal", alpha = alpha, size = size, color = COLOR
)
distance_center_development <- development_plot(
  dataset = distance_center, title = "Distance center", alpha = alpha, size = size, color = COLOR
)
line_center_development <- development_plot(
  dataset = line_center, title = "Line center", alpha = alpha, size = size, color = COLOR
)
line_edge_development <- development_plot(
  dataset = line_edge, title = "Line edge", alpha = alpha, size = size, color = COLOR
)
random_development <- development_plot(
  dataset = random, title = "Random", alpha = alpha, size = size, color = COLOR
)
square_center_development <- development_plot(
  dataset = square_center, title = "Square center", alpha = alpha, size = size, color = COLOR
)
square_corner_development <- development_plot(
  dataset = square_corner, title = "Square corner", alpha = alpha, size = size, color = COLOR
)

ggarrange(
  corners_development, diagonal_development, distance_center_development, line_center_development,
  line_edge_development, random_development, square_center_development, square_corner_development,
  ncol = 2, nrow = 4
) +
  theme_axelfraud_arrange()

# saving ----
if(SAVE){ggsave(filename = here::here("figures", "development.png"), width = 10, height = 10, dpi = 300)}
```


```{r}
# generics ----
alpha <- 0.05
size <- 2
binwidth <- 1

# create grid plots ----
line_edge_grid_plot <- grid_df %>% grid_plot(x = "x", y = "y", color = "line_edge")
line_center_grid_plot <- grid_df %>% grid_plot(x = "x", y = "y", color = "line_center")
square_corner_grid_plot <- grid_df %>% grid_plot(x = "x", y = "y", color = "square_corner")
square_center_grid_plot <- grid_df %>% grid_plot(x = "x", y = "y", color = "square_center")
random_grid_plot <- grid_df %>% grid_plot(x = "x", y = "y", color = "random")
corners_grid_plot <- grid_df %>% grid_plot(x = "x", y = "y", color = "corners")
diagonal_grid_plot <- grid_df %>% grid_plot(x = "x", y = "y", color = "diagonal")
distance_center_grid_plot <- grid_df %>% grid_plot(x = "x", y = "y", color = "distance_center")

# create development plots ----
corners_development <- development_plot(
  dataset = corners, title = element_blank(), alpha = alpha, size = size, color = COLOR
) 
diagonal_development <- development_plot(
  dataset = diagonal, title = element_blank(), alpha = alpha, size = size, color = COLOR
)
distance_center_development <- development_plot(
  dataset = distance_center, title = element_blank(), alpha = alpha, size = size, color = COLOR
)
line_center_development <- development_plot(
  dataset = line_center, title = element_blank(), alpha = alpha, size = size, color = COLOR
)
line_edge_development <- development_plot(
  dataset = line_edge, title = element_blank(), alpha = alpha, size = size, color = COLOR
)
random_development <- development_plot(
  dataset = random, title = element_blank(), alpha = alpha, size = size, color = COLOR
)
square_center_development <- development_plot(
  dataset = square_center, title = element_blank(), alpha = alpha, size = size, color = COLOR
)
square_corner_development <- development_plot(
  dataset = square_corner, title = element_blank(), alpha = alpha, size = size, color = COLOR
)

# create distribution plots ----
corners_distribution <- distribution_plot(
  dataset = corners, title = element_blank(), binwidth = binwidth, color = COLOR
)
diagonal_distribution <- distribution_plot(
  dataset = diagonal, title = element_blank(), binwidth = binwidth, color = COLOR
)
distance_center_distribution <- distribution_plot(
  dataset = distance_center, title = element_blank(), binwidth = binwidth, color = COLOR
)
line_center_distribution <- distribution_plot(
  dataset = line_center, title = element_blank(), binwidth = binwidth, color = COLOR
)
line_edge_distribution <- distribution_plot(
  dataset = line_edge, title = element_blank(), binwidth = binwidth, color = COLOR
)
random_distribution <- distribution_plot(
  dataset = random, title = element_blank(), binwidth = binwidth, color = COLOR
)
square_center_distribution <- distribution_plot(
  dataset = square_center, title = element_blank(), binwidth = binwidth, color = COLOR
)
square_corner_distribution <- distribution_plot(
  dataset = square_corner, title = element_blank(), binwidth = binwidth, color = COLOR
)

# arrange and save plots (part 1) ----
ggarrange(
  line_edge_grid_plot, line_edge_development, line_edge_distribution,
  line_center_grid_plot, line_center_development, line_center_distribution,
  square_corner_grid_plot, square_corner_development, square_corner_distribution,
  square_center_grid_plot, square_center_development, square_center_distribution,
  ncol = 3, nrow = 4
) +
  theme_axelfraud_arrange(plot_margin = 15)

if(SAVE){ggsave(filename = here::here("figures", "full_visual_analysis_a.png"), width = 14, height = 14, dpi = 300)}

# arrange and save plots (part 2) ----
ggarrange(
  random_grid_plot, random_development, random_distribution,
  corners_grid_plot, corners_development, corners_distribution,
  diagonal_grid_plot, diagonal_development, diagonal_distribution,
  distance_center_grid_plot, distance_center_development, distance_center_distribution,
  ncol = 3, nrow = 4
) +
  theme_axelfraud_arrange(plot_margin = 15)

if(SAVE){ggsave(filename = here::here("figures", "full_visual_analysis_b.png"), width = 14, height = 14, dpi = 300)}

```



```{r, eval=FALSE}
# for powerpoint ----
library(scales)
show_col(grey_pal(0, 1)(10))
```


```{r, eval=FALSE}
line_edge %>% by_class("line_edge") %>% 
  rbind(line_center %>% by_class("line_center")) %>% 
  rbind(square_corner %>% by_class("square_corner")) %>% 
  rbind(square_center %>% by_class("square_center")) %>% 
  rbind(random %>% by_class("random")) %>% 
  rbind(corners %>% by_class("corners")) %>% 
  rbind(diagonal %>% by_class("diagonal")) %>% 
  rbind(distance_center %>% by_class("distance_center")) -> tmp

tmp %>% 
  group_by(config) %>% 
  summarize(
    agreement = agreement(count),
    polarization = polarization(count),
    consensus = consensus(count),
    BerryMielke = BerryMielke(count),
    BlairLacy = BlairLacy(count)
  ) %>% 
  ungroup()

```

```{r}
# compute agreements over time ----
square_corner %>% agreement_by_step() -> square_corner_agreement
square_center %>% agreement_by_step() -> square_center_agreement
corners %>% agreement_by_step() -> corners_agreement
line_edge %>% agreement_by_step() -> line_edge_agreement
line_center %>% agreement_by_step() -> line_center_agreement
diagonal %>% agreement_by_step() -> diagonal_agreement
distance_center %>% agreement_by_step() -> distance_center_agreement
random %>% agreement_by_step() -> random_agreement

# plotting ----
square_corner_agreement %>% 
  ggplot(aes(x = step, y = agreement)) +
    geom_hline(yintercept = 0, size = 1.5, color = "grey40") +
    geom_line(size = 2, alpha = 0.7, color = COLOR) +
    scale_y_continuous(limits = c(-1, 1)) +
    labs(title = "Square corner", x = "Step", y = "Agreement") +
    theme_axelfraud() +
    theme(axis.title = element_text(size = 12)) -> square_corner_agreement_plot

square_center_agreement %>% 
  ggplot(aes(x = step, y = agreement)) +
    geom_hline(yintercept = 0, size = 1.5, color = "grey40") +
    geom_line(size = 2, alpha = 0.7, color = COLOR) +
    scale_y_continuous(limits = c(-1, 1)) +
    labs(title = "Square center", x = "Step", y = "Agreement") +
    theme_axelfraud() +
    theme(axis.title = element_text(size = 12)) -> square_center_agreement_plot

corners_agreement %>% 
  ggplot(aes(x = step, y = agreement)) +
    geom_hline(yintercept = 0, size = 1.5, color = "grey40") +
    geom_line(size = 2, alpha = 0.7, color = COLOR) +
    scale_y_continuous(limits = c(-1, 1)) +
    labs(title = "Corners", x = "Step", y = "Agreement") +
    theme_axelfraud() +
    theme(axis.title = element_text(size = 12)) -> corners_agreement_plot

line_edge_agreement %>% 
  ggplot(aes(x = step, y = agreement)) +
    geom_hline(yintercept = 0, size = 1.5, color = "grey40") +
    geom_line(size = 2, alpha = 0.7, color = COLOR) +
    scale_y_continuous(limits = c(-1, 1)) +
    labs(title = "Line edge", x = "Step", y = "Agreement") +
    theme_axelfraud() +
    theme(axis.title = element_text(size = 12)) -> line_edge_agreement_plot

line_center_agreement %>% 
  ggplot(aes(x = step, y = agreement)) +
    geom_hline(yintercept = 0, size = 1.5, color = "grey40") +
    geom_line(size = 2, alpha = 0.7, color = COLOR) +
    scale_y_continuous(limits = c(-1, 1)) +
    labs(title = "Line center", x = "Step", y = "Agreement") +
    theme_axelfraud() +
    theme(axis.title = element_text(size = 12)) -> line_center_agreement_plot

diagonal_agreement %>% 
  ggplot(aes(x = step, y = agreement)) +
    geom_hline(yintercept = 0, size = 1.5, color = "grey40") +
    geom_line(size = 2, alpha = 0.7, color = COLOR) +
    scale_y_continuous(limits = c(-1, 1)) +
    labs(title = "Diagonal", x = "Step", y = "Agreement") +
    theme_axelfraud() +
    theme(axis.title = element_text(size = 12)) -> diagonal_agreement_plot

distance_center_agreement %>% 
  ggplot(aes(x = step, y = agreement)) +
    geom_hline(yintercept = 0, size = 1.5, color = "grey40") +
    geom_line(size = 2, alpha = 0.7, color = COLOR) +
    scale_y_continuous(limits = c(-1, 1)) +
    labs(title = "Distance center", x = "Step", y = "Agreement") +
    theme_axelfraud() +
    theme(axis.title = element_text(size = 12)) -> distance_center_agreement_plot

random_agreement %>% 
  ggplot(aes(x = step, y = agreement)) +
    geom_hline(yintercept = 0, size = 1.5, color = "grey40") +
    geom_line(size = 2, alpha = 0.7, color = COLOR) +
    scale_y_continuous(limits = c(-1, 1)) +
    labs(title = "Random", x = "Step", y = "Agreement") +
    theme_axelfraud() +
    theme(axis.title = element_text(size = 12)) -> random_agreement_plot

# arrange plots and save ----
ggarrange(
  random_agreement_plot, distance_center_agreement_plot, diagonal_agreement_plot, line_edge_agreement_plot, 
  ncol = 1, nrow = 4
)

if(SAVE){ggsave(filename = here::here("figures", "agreement_over_time_a.png"), width = 7, height = 10, dpi = 300)}

ggarrange(
  line_center_agreement_plot, square_corner_agreement_plot, square_center_agreement_plot, corners_agreement_plot,
  ncol = 1, nrow = 4
)

if(SAVE){ggsave(filename = here::here("figures", "agreement_over_time_b.png"), width = 7, height = 10, dpi = 300)}
```



# Measurements

shortterm:

  * van der Eijk's A (measurement of agreement)
  * refer to https://en.wikipedia.org/wiki/Multimodal_distribution for other measurements  
  * stubborn threshold value? (at some point -> stubborn culture wins?)
  * fit logistic curve to different replicates -> find turning point
  * activity parameter (comparison with last step)
  * agrmt package -> other measures

longterm:
  
  * manipulate stubborn count
  * other network types
  * informed agents
  * interval scale for cultures



## Unique Cultures

```{r, eval=FALSE}
color_scheme <- viridis(300, option = "plasma")
color_scheme2 <- rep(COLOR, 300)

data %>% 
  group_by(step, replicate, culture) %>% 
  summarize(count = n()) %>% 
  ungroup() %>% 
  group_by(step, replicate) %>% 
  summarize(unique_cultures = n()) %>% 
  ungroup() -> tmp

tmp %>% 
  ggplot(aes(x = step, y = unique_cultures, color = as.factor(replicate))) +
  geom_line(alpha = 0.05, size = 2) +
  scale_color_manual(values = color_scheme2) +
  labs(
    title = "Development of unique culture count",
    x = "Step",
    y = "Unique cultures"
  ) +
  theme(legend.position = "None") +
  theme_axelfraud()

if(SAVE){ggsave(filename = "unique_cultures.png", width = 10, height = 4, dpi = 300)}
```
























